Air cargo load and route planning in pickup and delivery operations

### 2023-06-03 CAIE/old.tex
CAIE paper transferred to parallel folder

% !TeX spellcheck = en_GB
\documentclass[preprint,authoryear]{elsarticle}

\usepackage[left]{lineno}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{multirow}

@@

\usepackage{caption}
\captionsetup{labelfont=bf}
\captionsetup{skip=0pt} % vertical distance from the table or figure

@@

\usepackage[normalem]{ulem}
\usepackage{xcolor}

@@

%----- begin celio
\usepackage{scrextend}
\newcommand{\boldm}[1] {\mathversion{bold}#1\mathversion{normal}}
\newcommand{\round}[1]{\ensuremath{\lfloor#1\rceil}}
\usepackage{setspace}
\usepackage{array}
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}

@@

%----- end celio

\journal{European Journal of Operational Research}

@@

In the scenario of aerial pickup and delivery of goods in a distribution network, transport aviation faces risks of cargo unbalancing due to the urgency required for loading for rapid take-off and mission accomplishment, especially in times of crisis, public calamity, client contract short lead times, or any external pressure for immediate take-off. Also, there is no technological assistance to help the load and trip planners with the huge number of demands for transport in each hub. This enables other risks such as improper delivery, excessive fuel burn, and longer than necessary turn-around time. We contributed by modelling and solving a new problem of planning the loading and routing of an aircraft according to a utility score, weight and balance principles, and fuel consumption in a tour of simultaneous pickup and delivery at intermediate hubs. This new hard problem, named {\it Air Cargo Load Planning with Routing, Pickup, and Delivery Problem (ACLP+RPDP)}, is mathematically modelled using standardised pallets in fixed positions, obeying the centre of gravity constraints, delivering each item to its destination, and minimising fuel consumption costs. We also contributed by carrying out multiple experiments with a commercial solver and four well-known meta-heuristics on synthetic data based on real data from the {\it Brazilian Air Force}\/ transportation history. These challenging benchmark instances are made publicly available. We also created a heuristic that quickly finds good solutions for a wide range of problem sizes, an essential contribution as it was the unique method that managed to solve all testing scenarios.

% Reescrever

@@

\begin{keyword}
Air Cargo \sep Load Planning \sep Air Palletization \sep Weight and Balance \sep Pickup and Delivery \sep Vehicle Routing
\end{keyword}

@@

Air cargo transport involves several sub-problems that are difficult to solve. Recently, \cite[p. 401]{BrandtStefan2019} defined the {\it Air Cargo Load Planning Problem} (ACLPP) as four sub-problems: {\it Aircraft Configuration Problem} (ACP), {\it Build-up Scheduling Problem} (BSP), {\it Air Cargo Palletization Problem} (APP) and {\it Weight and Balance Problem} (WBP). Several aspects were considered in this modelling: characteristics of the items to be transported (dimensions, scores, dangerousness, etc.); types and quantities of {\it unit load devices} (ULDs), commonly called pallets; when these pallets are assembled; how items are allocated to pallets; in which positions these pallets are to be placed; how the total cargo weight is balanced; etc. They also presented a comprehensive bibliographic survey of solving methods that had been developed in different situations.

However, there are still other important challenges in air cargo transport that go beyond the definition of the ACLPP, especially with regard to the flight itinerary and the loading and unloading at each destination (or node) of this travel plan. In this context, at least two more important sub-problems can be considered: pickup and delivery operations at each node, called {\it Pickup and Delivery Problem} (PDP), and the search for the lowest cost route, which is the well-known {\it Travelling Salesman Problem} (TSP).

Considering air cargo transport, Table \ref{tab:sa} lists the main works in the literature and the corresponding sub-problems addressed. We also indicate whether the dimensions of the items were taken into account ({\bf 3D} or {\bf 2D}) and which solution method was used: heuristics ({\bf Heu}), integers ({\bf Int}), or linear programming ({\bf Lin}).

\begin{table}[H]
	\centering
	\caption{Air cargo transport: literature, problems and features}  \label{tab:sa}
	\scriptsize
	\renewcommand{\arraystretch}{1.1} % alturas das linhas
	\begin{tabular}{r|cc|cc|cc|ccc}
		\toprule
		                            & {\bf APP}  & {\bf WBP}  &  {\bf PDP}   &{\bf TSP}   & {\bf 2D}  & {\bf 3D}  & {\bf Heu}  & {\bf Int}  & {\bf Lin} \\
		\midrule
		\cite{LarsenMikkelsen1979}  & $.$        & $\bigstar$ & $.$          & $.$        & $.$       & $.$       & $\bigstar$ & $.$        &  $.$ \\
		\cite{Brosh1981}  & $.$ & $\bigstar$  & $.$   & $.$ & $.$ & $.$   & $.$  & $.$  &  $\bigstar$ \\
		\cite{Kevin1992}  & $.$ & $\bigstar$  & $.$ & $.$ & $.$ &$.$   & $.$  & $\bigstar$  &  $.$ \\
		\cite{Heidelberg1998}  & $.$ & $\bigstar$  & $.$ & $.$ & $\bigstar$ &$.$   & $\bigstar$  & $.$  &  $.$ \\
		\cite{MongeauBes2003}    & $\bigstar$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\
		\cite{fok2004optimizing} & $.$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\	
		\cite{Chan2006}  & $\bigstar$ & $.$    & $.$ & $.$ & $.$ & $\bigstar$  & $\bigstar$  & $.$  &  $.$ \\
		\cite{KaluznyBohdanL2009Oalb}  & $.$ & $\bigstar$  & $.$  & $.$ & $\bigstar$ &$.$  & $.$  & $\bigstar$  &  $.$ \\
		\cite{Verstichel2011}   & $.$ & $\bigstar$    & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\
		\cite{MesquitaCunha2011}   & $.$ & $.$    & $\bigstar$ & $.$ & $.$ & $.$   & $\bigstar$  & $.$  &  $.$ \\		
		\cite{Limbourg2012} & $.$ & $\bigstar$  & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\
		\cite{RoesenerHall2014}  & $\bigstar$ & $\bigstar$  & $.$  & $.$ & $.$ & $\bigstar$   & $.$  & $\bigstar$  &  $.$ \\
		\cite{Vancroonemburg2014}  & $\bigstar$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\
		\cite{LurkinSchyns2015} & $.$ & $\bigstar$  & $\bigstar$ & $.$  & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\
		\cite{RoesenerBarnes2016}  & $.$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $\bigstar$  & $.$  &  $.$ \\
		\cite{PaquaySchynsLimbourg2016,PaquayLimbourgSchynsOliveira2018}  & $\bigstar$ & $\bigstar$ & $.$ & $.$ & $.$ & $\bigstar$ & $\bigstar$  & $\bigstar$ & $.$ \\
		\cite{YangLiuGao2018} & $.$ & $\bigstar$  & $.$  & $.$ & $\bigstar$  & $.$ & $\bigstar$ & $.$  & $.$ \\
		\cite{wong2020} & $\bigstar$  & $\bigstar$  & $.$  & $.$   & $.$  & $.$ & $.$ & $\bigstar$  & $.$  \\
		\cite{eugene2021} & $\bigstar$ & $\bigstar$ & $.$  & $.$   & $.$ & $.$ & $.$ & $\bigstar$  & $.$  \\
		\cite{zhao2021} & $.$ & $\bigstar$ & $.$  & $.$  & $.$ & $.$ & $.$  & $\bigstar$ &  $.$ \\
		{\bf This work}   & $\bigstar$ & $\bigstar$  & $\bigstar$& $\bigstar$ & $.$ & $.$ & $\bigstar$ & $\bigstar$   &  $.$  \\
		\bottomrule 
	\end{tabular}
	\normalsize 
\end{table}

As can be seen, so far \cite{LurkinSchyns2015} is the only work that simultaneously addresses an air cargo (WBP) and a flight itinerary (PDP) sub-problem. Although it is innovative, strong simplifications were imposed by the authors: in relation to loading, APP was ignored; with regard to routing, it is assumed a pre-defined flight plan restricted to two legs. It is important to note that these authors consider an aircraft with two doors, and the minimization of loading and unloading costs at the intermediate node was modelled through a container sequencing problem. Referring directly to this work, \cite[p. 409]{BrandtStefan2019} comment: {\it However, not even these sub-problems are acceptably solved for real-world problem sizes or the models omit some practically relevant constraints}.

There are real situations that are much more complex. In this work, we consider a practical case in Brazil, which is the largest economy in Latin America. Due to its dimensions, this country has the largest air market on the continent with $2,499$\/ registered airports, of which $1,911$\/ are private and $588$\/ are public. Although it is an immense distribution network, airlift missions consider 3 to 5 nodes per flight plan. Throughout this work, we address routes with up to 7 nodes, as can be seen in Table \ref{tab:costs} and Figure \ref{fig:nodes}.

@@

	\end{minipage}\hfill % these two lines must be close to each other
	\begin{minipage}{0.45\linewidth}

		\caption{Brazilian airports distances ($km$)}  \label{tab:costs}
		\centering

		\footnotesize

		\newcolumntype{Y}{>{\centering\arraybackslash}p{0.09\textwidth}}
		\newcolumntype{X}{>{\centering}p{0.09\textwidth}}

@@

	\end{minipage}\hfill % these two lines must be close to each other
	\begin{minipage}{0.50\linewidth}
		\centering
		\includegraphics[scale=0.25]{Images/nodes.png}
		\captionof{figure}{A route between Brazilian airports}
		\label{fig:nodes}		
	\end{minipage}
\end{table}

In the {\it Brazilian Air Force}\/ missions, hundreds of items can be carried at each node, where the objectives are to prioritise the transport of the most important items and minimise the cost of fuel along the route. As standardised pallets are used with predefined positions on the aircraft, it is possible to carry out loading and unloading at each node in around two hours. However, there is no technological assistance that guarantees the achievement of these objectives.

This work proposes a method that attends these objectives: a pallet building and arrangement plan with a routing option that maximises the benefit-cost ratio for the smooth execution of pickup and delivery transport missions. We develop a heuristic that can be executed on a simple handheld computer (like a laptop or a tablet) and that provides a solution quickly enough to keep this cargo handling time under an hour. This heuristic will reduce the stress that transport planners are subjected to, because they have to deal with a lot of information in planning the aircraft route, assembling the pallets, and picking up and delivering at each node. To the best of our knowledge, this is the first time that an air cargo transport problem that simultaneously involves APP, WBP, PDP and TSP has been addressed. This new problem is named {\it Air Cargo Load Planning with Routing, Pickup and Delivery Problem} (ACLP+RPDP).

This article is organised into six more sections. In Section \ref{sec2}, we give a brief review of the literature. In Section \ref{sec3}, we present the problem context and assumptions and, in Section \ref{sec4}, the mathematical model and how we dealt with its issues. In Section \ref{sec5}, we describe the elaborate algorithms, whose results are presented in Section \ref{sec6}. Finally, our conclusions are in Section \ref{sec7}.

@@

\cite{LarsenMikkelsen1979} developed an interactive procedure for loading 14 types of Boeing 747 into a two-leg flight plan. Seven types of items were considered to be allocated in 17 to 42 positions. With non-linear programming and heuristics, they present a solution that minimises positioning changes in the intermediate node, optimising the load balancing in the aircraft.

\cite{Brosh1981} addressed the problem of planning the allocation of cargo on an aircraft. Considering volume, weight and structural constraints, the author finds the optimal load layout through a fractional programming problem.

\cite{Kevin1992} developed a multi-criteria optimization approach to load the {\it C-130} aircraft of the {\it Canadian Air Force}. Based on integer programming, this model provides timely planning and improves airlift support for combat operations, solving WBP with pallets in fixed positions, and considering 20 different items.

\cite{Heidelberg1998} developed a heuristic for 2D packing in air loading, comparing it with methods for solving the {\it Bin Packing Problem}. Authors conclude that the classical algorithms are inadequate in this context, because they ignore the aircraft balancing constraints.

%\cite{Gueret2003} proposed a method for loading military aircraft (specifically, the french military) for airlift operations. They used a two-phased solution method consisting of heuristics that quickly compute suboptimal initial solutions for a 2-dimensional bin packing and a local search algorithm to improve upon the initial solution, while ignoring the aircraft center of gravity.

\cite{MongeauBes2003} presented a method based on linear integer programming to solve the problem of choosing and positioning containers on the {\it Airbus 340-300}. Safety and stability restrictions were considered, with the objective of minimising fuel consumption.

\cite{fok2004optimizing} developed a web-based application to make efficient use of space and load balancing for an air cargo company. Based on an analysis of historical data, an operational load planning with mathematical optimization is obtained. This container load planning is usually done roughly 2 hours before departure, when all cargo details are in place.

\cite{Chan2006} carried out a case study with heterogeneous pallets. In order to minimise the total cost of shipping, they developed a 3D packing heuristic, with a loading plan for each pallet. Although the authors do not consider load balancing or positioning of pallets in the cargo hold, this method is relevant in commercial and industrial applications, where cargo items tend to be less dense.

\cite{KaluznyBohdanL2009Oalb} developed a mixed integer linear programming model to arrange a set of items in a military context that optimises the load balance.

\cite{Verstichel2011} solved WBP by selecting the most profitable subset of containers to be loaded onto an aircraft using mixed-integer programming. Experimental results on real-life data showed significant improvements compared to those obtained manually by an experienced planner.

\cite{MesquitaCunha2011} presented a heuristic for a real problem of the {\it Brazilian Air Force}, which consists of defining transport routes with simultaneous collection and delivery from a central distribution terminal.

\cite{Limbourg2012} developed a mixed-integer program for optimally rearranging a set of pallets into a compartmentalised cargo aircraft, specifically the {\it Boeing 747}.

\cite{RoesenerHall2014} solved APP and WBP as an integer programming problem, which also allows items to be loaded into pallets according to a specific orientation (e.g., this side up).

\cite{Vancroonemburg2014} presented a mixed integer linear programming model that selects the most profitable pallets, satisfying safety and load balancing constraints on the {\it Boeing 747-400}. Using a solver, authors solved real problems in less than an hour.

As already mentioned, \cite{LurkinSchyns2015} was the first work that simultaneously modelled WBP and PDP in air cargo transport. The authors demonstrated that this problem is NP-hard and performed some experiments with real data, noting that their model offers better results than those obtained manually.

\cite{RoesenerBarnes2016} proposed a heuristic to solve the {\it Dynamic Airlift Loading Problem} (DALP). Given a set of palletized cargo items that require transport between two nodes in a time frame, the objective of this problem is to select an efficient subset of aircraft, partition the pallets into aircraft loads and assign them to allowable positions on those aircraft.

\cite{PaquaySchynsLimbourg2016} presented a mathematical modelling to optimise the loading of heterogeneous 3D boxes on pallets with a truncated parallelepipeds format. Its objective is to maximise the volume used in containers, considering load balancing restrictions, the presence of fragile items and the possibility of rotating these boxes. \cite{PaquayLimbourgSchynsOliveira2018} developed some heuristics to solve this problem.

\cite{YangLiuGao2018} modelled the air transport problem as a 2D packing problem, and presented a heuristic for its optimization in several aircraft, considering load balancing in order to minimise fuel consumption.

\cite{wong2020}A developed a mathematical model and a tool based on mixed integer programming for optimising cargo in aircraft with different pallet configurations. Balance restrictions and the presence of dangerous items were considered. \cite{eugene2021} integrated this tool to a digital simulation model, with a visualisation and validation system, based on sensors that alert about load deviations.

\cite{zhao2021} proposed a new modelling for WBP based on mixed integer programming. Instead of focusing on the centre of gravity (CG) deviation, the authors consider the original CG envelope of the aircraft, with a linearization method for its non-linear constraints.

As can be seen, none of these works address air cargo palletization and load balancing with route optimization in a multi-leg flight plan. This is the objective of our work: to model and elaborate heuristics for a real problem that simultaneously involves 4 intractable sub-problems: APP, WBP, PDP and TSP.

@@

As we are dealing with an extremely complex and diverse problem, we decided to establish some simplifying characteristics:

@@

	\item At each node of the flight plan, the items to be allocated are characterised by weight, volume, scores, and previously known destinations, but do not have dimensions. We leave the consideration of 2D or 3D items for future work.

	\item We also disregarded {\it hazardous} items, which eventually could be treated as high score items and other specific constraints.

@@

	\item Finally, as we are interested in minimising fuel costs, we disregarded some lower ones as {\it handling operation costs}.

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.4]{Images/large.png}
	\caption{Consolidated items on pallets inside a {\it Boeing C-17}}
	\small\textsuperscript{Source: https://www.sacprogram.org/en/Pages/Boeing-C-17-Globemaster-III.aspx}
	\label{fig:larger2}
\end{figure}

@@

	\caption{Smaller aircraft layout}
	%\small\textsuperscript{Source: the author}	
	\label{fig:smaller}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.22]{Images/lateral.png}
	\caption{Aircraft longitudinal cut showing red lines as pallets}
	%\small\textsuperscript{Source: the author}
	\label{fig:lateral}
\end{figure}

>>>>

% !TeX spellcheck = en_US
%\documentclass[preprint,authoryear]{elsarticle}
\documentclass[preprint]{elsarticle}
% sudo apt-get install -y texlive-publishers

\usepackage[left]{lineno}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{multirow}

@@

\usepackage{caption}
\captionsetup{labelfont=bf}
\captionsetup{skip=0pt}

@@

\usepackage[normalem]{ulem}
%\usepackage{xcolor}

@@

\usepackage{scrextend}
\newcommand{\boldm}[1] {\mathversion{bold}#1\mathversion{normal}}
\newcommand{\round}[1]{\ensuremath{\lfloor#1\rceil}}
\usepackage{setspace}
\usepackage{array}
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}
\hyphenation{cost-ef-fec-tive-ness}

@@

\journal{Computers \& Operations Research}

@@

In aerial pickup and delivery of goods in a distribution network, transport aviation faces risks of cargo unbalancing due to the urgency required for loading, for fast take-off, and mission accomplishment, especially in times of crisis, public calamity, short deadlines for contracting customers, or any external pressure for immediate take-off. In addition, there is no technological assistance to help the load and trip planners with the huge number of demands for transport in each hub. This enables other risks, such as improper delivery, excessive fuel burn, and longer than necessary turn-around time. We defined and solved the problem of planning the loading and routing of an aircraft according to a utility score, weight and balance principles, and fuel consumption in a tour of simultaneous pickup and delivery at intermediate hubs. This NP-hard problem, named {\it Air Cargo Load Planning with Routing, Pickup, and Delivery Problem (ACLP+RPDP)}, is mathematically modeled using standardized pallets in fixed positions, obeying center of gravity constraints, delivering each item to its destination, and minimizing fuel consumption costs. We performed multiple experiments with a commercial solver and well-known meta-heuristics on data based on the transport history of the {\it Brazilian Air Force}, and also designed a new method that quickly finds good solutions for a wide range of problem sizes, which solved all test scenarios within an acceptable operational runtime.

@@

\begin{keyword}
Load Planning \sep Air Palletization \sep Weight and Balance \sep Pickup and Delivery \sep Vehicle Routing
\end{keyword}

@@

Air cargo transport involves several sub-problems that are difficult to solve. Recently, Brandt and Nickel \cite[p. 401]{BrandtStefan2019} defined the {\it Air Cargo Load Planning Problem} (ACLPP) as four sub-problems: {\it Aircraft Configuration Problem} (ACP), {\it Build-up Scheduling Problem} (BSP), {\it Air Cargo Palletization Problem} (APP) and {\it Weight and Balance Problem} (WBP). Several aspects were considered in this modeling: characteristics of the items to be transported (dimensions, scores, dangerousness, etc.); types and quantities of {\it unit load devices} (ULDs), commonly called pallets; when these pallets are assembled; how items are allocated to pallets; in which positions these pallets are to be placed; how the total cargo weight is balanced; etc. They also presented a comprehensive bibliographic survey of solving methods that had been developed in different situations.

However, there are still other important challenges in air cargo transport that go beyond the definition of the ACLPP, especially with regard to the flight itinerary and the loading and unloading at each destination (or node) of this travel plan. In this context, at least two more important sub-problems can be considered: pickup and delivery operations at each node, called {\it Pickup and Delivery Problem} (PDP), and the search for the lowest cost route, which is the well-known {\it Traveling Salesman Problem} (TSP).

Considering air cargo transport, Table \ref{tab:sa} lists the main works in the literature in chronological order, and the corresponding sub-problems addressed. We also indicate whether the dimensions of the items were taken into account ({\bf 3D} or {\bf 2D}) and which solution method was used: heuristics ({\bf Heu}), integers ({\bf Int}), or linear programming ({\bf Lin}).

\begin{table}[H]
	\centering
	\caption{Air cargo transport: literature, problems and features}  \label{tab:sa}
	\scriptsize
	\renewcommand{\arraystretch}{1.1} 
	\begin{tabular}{r|cc|cc|cc|ccc}
		\toprule
		 Work & {\bf APP}  & {\bf WBP}  &  {\bf PDP}   &{\bf TSP}   & {\bf 2D}  & {\bf 3D}  & {\bf Heu}  & {\bf Int}  & {\bf Lin} \\
		\midrule
		Larsen and Mikkelsen \cite{LarsenMikkelsen1979}  & $.$        & $\bigstar$ & $.$          & $.$        & $.$       & $.$       & $\bigstar$ & $.$        &  $.$ \\
		Brosh \cite{Brosh1981}  & $.$ & $\bigstar$  & $.$   & $.$ & $.$ & $.$   & $.$  & $.$  &  $\bigstar$ \\
		Ng \cite{Kevin1992}  & $.$ & $\bigstar$  & $.$ & $.$ & $.$ &$.$   & $.$  & $\bigstar$  &  $.$ \\
		Heidelberg {\it et al.} \cite{Heidelberg1998}  & $.$ & $\bigstar$  & $.$ & $.$ & $\bigstar$ &$.$   & $\bigstar$  & $.$  &  $.$ \\
		Mongeau and Bes \cite{MongeauBes2003}    & $\bigstar$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\
		Fok and Chun \cite{fok2004optimizing} & $.$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\	
		Chan {\it et al.} \cite{Chan2006}  & $\bigstar$ & $.$    & $.$ & $.$ & $.$ & $\bigstar$  & $\bigstar$  & $.$  &  $.$ \\
		Kaluzny and Shaw \cite{KaluznyBohdanL2009Oalb}  & $.$ & $\bigstar$  & $.$  & $.$ & $\bigstar$ &$.$  & $.$  & $\bigstar$  &  $.$ \\
		Verstichel {\it et al.} \cite{Verstichel2011}   & $.$ & $\bigstar$    & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\
		Mesquita and Cunha \cite{MesquitaCunha2011}   & $.$ & $.$    & $\bigstar$ & $.$ & $.$ & $.$   & $\bigstar$  & $.$  &  $.$ \\		
		Limbourg {\it et al.} \cite{Limbourg2012} & $.$ & $\bigstar$  & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\
		Roesener and Barnes \cite{RoesenerHall2014}  & $\bigstar$ & $\bigstar$  & $.$  & $.$ & $.$ & $\bigstar$   & $.$  & $\bigstar$  &  $.$ \\
		Vancroonenburg {\it et al.} \cite{Vancroonenburg2014}  & $\bigstar$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\
		Lurkin and Schyns \cite{LurkinSchyns2015} & $.$ & $\bigstar$  & $\bigstar$ & $.$  & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ \\
		Roesener and Barnes \cite{RoesenerBarnes2016}  & $.$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $\bigstar$  & $.$  &  $.$ \\
		Paquay {\it et al} \cite{PaquaySchynsLimbourg2016,PaquayLimbourgSchynsOliveira2018}  & $\bigstar$ & $\bigstar$ & $.$ & $.$ & $.$ & $\bigstar$ & $\bigstar$  & $\bigstar$ & $.$ \\
		Chenguang {\it el al.} \cite{YangLiuGao2018} & $.$ & $\bigstar$  & $.$  & $.$ & $\bigstar$  & $.$ & $\bigstar$ & $.$  & $.$ \\
		Wong and Ling \cite{wong2020} & $\bigstar$  & $\bigstar$  & $.$  & $.$   & $.$  & $.$ & $.$ & $\bigstar$  & $.$  \\
		Wong {\it et al.} \cite{eugene2021} & $\bigstar$ & $\bigstar$ & $.$  & $.$   & $.$ & $.$ & $.$ & $\bigstar$  & $.$  \\
		Zhao {\it et al.} \cite{zhao2021} & $.$ & $\bigstar$ & $.$  & $.$  & $.$ & $.$ & $.$  & $\bigstar$ &  $.$ \\
		{\bf This article}   & $\bigstar$ & $\bigstar$  & $\bigstar$& $\bigstar$ & $.$ & $.$ & $\bigstar$ & $\bigstar$   &  $.$  \\
		\bottomrule 
	\end{tabular}
	\normalsize 
\end{table}

As can be seen, so far Lurkin and Schyns \cite{LurkinSchyns2015} is the only work that simultaneously addresses an air cargo (WBP) and a flight itinerary (PDP) sub-problem. Although it is innovative, strong simplifications were imposed by the authors: in relation to loading, APP was ignored; with regard to routing, it is assumed a pre-defined tour plan restricted to two legs. It is important to note that these authors consider an aircraft with two doors, and the minimization of loading and unloading costs at the intermediate node was modeled through a container sequencing problem. Referring directly to this work, Brandt and Nickel \cite[p. 409]{BrandtStefan2019} comment: {\it However, not even these sub-problems are acceptably solved for real-world problem sizes or the models omit some practically relevant constraints}.

There are real situations that are much more complex. In this work, we consider a practical case in Brazil, which is the largest economy in Latin America. Due to its dimensions, this country has the largest air market on the continent with $2,499$\/ registered airports, of which $1,911$\/ are private and $588$\/ are public. Although it is an immense distribution network, airlift missions consider 3 to 5 nodes per tour plan. Throughout this work, we address routes with up to 7 nodes, as can be seen in Table \ref{tab:costs} and Figure \ref{fig:nodes}.

@@

	\end{minipage}\hfill 
	\begin{minipage}{0.45\linewidth}

		\caption{Brazilian airports distances ($km$)}  \label{tab:costs}
		\centering
		\footnotesize
		\newcolumntype{Y}{>{\centering\arraybackslash}p{0.09\textwidth}}
		\newcolumntype{X}{>{\centering}p{0.09\textwidth}}

@@

	\end{minipage}\hfill 
	\begin{minipage}{0.50\linewidth}
		\centering
		\includegraphics[scale=0.25]{Images/nodes.png}
		\captionof{figure}{A route with some Brazilian airports}
		\label{fig:nodes}		
	\end{minipage}
\end{table}

In the {\it Brazilian Air Force}\/ missions, hundreds of items can be carried at each node, where the objectives are to prioritise the transport of the most important items and minimize the cost of fuel along the route. As standardized pallets are used with predefined positions on the aircraft, it is possible to carry out loading and unloading at each node in around two hours. However, there is no technological assistance that guarantees the achievement of these objectives.

This work proposes a method that attends these objectives: a pallet building and arrangement plan with a routing option that maximizes the benefit-cost ratio for the smooth execution of pickup and delivery transport missions. We develop a method that can be executed on a simple handheld computer (like a laptop or a tablet) and that provides a solution quickly enough to keep this cargo handling time under an hour. This method will reduce the stress that transport planners are subjected to, because they have to deal with a lot of information in planning the aircraft route, assembling the pallets, and picking up and delivering at each node. To the best of our knowledge, this is the first time that an air cargo transport problem that simultaneously involves APP, WBP, PDP and TSP has been addressed. This new problem is named {\it Air Cargo Load Planning with Routing, Pickup and Delivery Problem} (ACLP+RPDP).

This article is organized into six more sections. In Section \ref{sec2}, we give a brief review of the literature. In Section \ref{sec3}, we present the problem context and assumptions, and in Section \ref{sec4}, we describe the mathematical model and how we dealt with its issues. In Section \ref{sec5}, we describe the elaborate algorithms, whose results are presented in Section \ref{sec6}. Finally, our conclusions are in Section \ref{sec7}.

@@

Larsen and Mikkelsen \cite{LarsenMikkelsen1979} developed an interactive procedure for loading 14 types of Boeing 747 into a two-leg transportation plan. Seven types of items were considered to be allocated in 17 to 42 positions. With non-linear programming and heuristics, they present a solution that minimizes positioning changes in the intermediate node, optimizing the load balancing in the aircraft.

Brosh \cite{Brosh1981} addressed the problem of planning the allocation of cargo on an aircraft. Considering volume, weight and structural constraints, the author finds the optimal load layout through a fractional programming problem.

Ng \cite{Kevin1992} developed a multi-criteria optimization approach to load the {\it C-130} aircraft of the {\it Canadian Air Force}. Based on integer programming, this model provides timely planning and improves airlift support for combat operations, solving WBP with pallets in fixed positions, and considering 20 different items.

Heidelberg {\it et al.} \cite{Heidelberg1998} developed a heuristic for 2D packing in air loading, comparing it with methods for solving the {\it Bin Packing Problem}. These authors conclude that the classical algorithms are inadequate in this context, because they ignore the aircraft balancing constraints.

Mongeau and Bes \cite{MongeauBes2003} presented a method based on linear integer programming to solve the problem of choosing and positioning containers in the {\it Airbus 340-300}. Safety and stability constraints were considered, with the objective of minimizing fuel consumption.

Fok and Chun \cite{fok2004optimizing} developed a web-based application to make efficient use of space and load balancing for an air cargo company. Based on an analysis of historical data, an operational load planning with mathematical optimization is obtained. This container load planning is usually done in roughly 2 hours before departure, when all cargo details are in place.

Chan {\it et al.} \cite{Chan2006} carried out a case study with heterogeneous pallets. In order to minimize the total cost of shipping, they developed a 3D packing heuristic, with a loading plan for each pallet. Although the authors do not consider load balancing or positioning of pallets in the cargo hold, this method is relevant in commercial and industrial applications, where cargo items tend to be less dense.

Kaluzny and Shaw \cite{KaluznyBohdanL2009Oalb} developed a mixed integer linear programming model to arrange a set of items in a military context that optimizes the load balance.

Verstichel {\it et al.} \cite{Verstichel2011} solved WBP by selecting the most profitable subset of containers to be loaded into an aircraft using mixed-integer programming. Experimental results on real-life data showed significant improvements compared to those obtained manually by an experienced planner.

Mesquita and Cunha \cite{MesquitaCunha2011} presented a heuristic for a real problem of the {\it Brazilian Air Force}, which consists of defining transport routes with simultaneous collection and delivery from a central distribution terminal.

Limbourg {\it et al.} \cite{Limbourg2012} developed a mixed-integer program for optimally rearranging a set of pallets into a compartmentalized cargo aircraft, specifically the {\it Boeing 747}.

Roesener and Hall \cite{RoesenerHall2014} solved APP and WBP as an integer programming problem, which also allows items to be loaded onto pallets according to a specific orientation (e.g., this side up).

Vancroonenbur {\it et al} \cite{Vancroonenburg2014} presented a mixed integer linear programming model that selects the most profitable pallets, satisfying safety and load balancing constraints on the {\it Boeing 747-400}. Using a solver, these authors solved real problems in less than an hour.

As already mentioned, Lurkin and Schyns \cite{LurkinSchyns2015} was the first work that simultaneously modeled WBP and PDP in air cargo transport. The authors demonstrated that this problem is NP-hard and performed some experiments with real data, noting that their model offers better results than those obtained manually.

Roesener and Barnes \cite{RoesenerBarnes2016} proposed a heuristic to solve the {\it Dynamic Airlift Loading Problem} (DALP). Given a set of palletized cargo items that require transport between two nodes in a time frame, the objective of this problem is to select an efficient subset of aircraft, partition the pallets into aircraft loads and assign them to allowable positions in those aircraft.

Paquay {\it et al.} \cite{PaquaySchynsLimbourg2016} presented a mathematical modeling to optimize the loading of heterogeneous 3D boxes on pallets with a truncated parallelepipeds format. Its objective is to maximize the volume used in containers, considering load balancing restrictions, the presence of fragile items and the possibility of rotating these boxes. Paquay {\it et al.} \cite{PaquayLimbourgSchynsOliveira2018} developed some heuristics to solve this problem.

Chenguang {\it et al.} \cite{YangLiuGao2018} modeled the air transport problem as a 2D packing problem, and presented a heuristic for its optimization in several aircraft, considering load balancing to minimize fuel consumption.

Wong and Ling \cite{wong2020}A developed a mathematical model and a tool based on mixed integer programming for optimizing cargo in aircraft with different pallet configurations. Balance constraints and the presence of dangerous items were considered. Wong {\it et al.} \cite{eugene2021} integrated this tool to a digital simulation model, with a visualization and validation system, based on sensors that alert about load deviations.

Zhao {\it et al.} \cite{zhao2021} proposed a new modeling for WBP based on mixed integer programming. Instead of focusing on the center of gravity (CG) deviation, the authors consider the original CG envelope of the aircraft, with a linearization method for its non-linear constraints.

As can be seen, none of these works address air cargo palletization and load balancing with route optimization in a multi-leg transportation plan. This is the objective of our work: to model and elaborate a solution for a real problem that simultaneously involves 4 intractable sub-problems: APP, WBP, PDP and TSP.

@@

As we are dealing with an extremely complex and diverse problem, we decided to establish some operational premises:

@@

	\item At each node of the tour plan, the items to be allocated are characterized by weight, volume, scores, and previously known destinations, but the dimensions are unknown. We leave the consideration of 2D or 3D items to a future work.

@@

	\item Finally, as we are interested in minimizing fuel costs, we disregarded some lower ones as {\it handling operation costs}. Other costs like this may be included in future work.

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.4]{Images/consolidated.jpg}
	\caption{Consolidated items on 463L pallets inside a {\it Boeing C-17}}
	\small\textsuperscript{Source: From Wikimedia Commons, the free media repository}
	\label{fig:larger2}
\end{figure}

@@

	\caption{Smaller aircraft layout}
	\label{fig:smaller}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.22]{Images/lateral.png}
	\caption{Aircraft longitudinal cut showing red lines as pallets}
	\label{fig:lateral}
\end{figure}
